Supporting Information : Effect of copula on extinction risk

### 2019-02-25 SuppMat.Rmd
plotting d upto 0.5

for(i in 1:dim(res_ricker_local)[3]){
  s<-res_ricker_local[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))

@@

for(i in 1:dim(res_ricker_global)[3]){
  s<-res_ricker_global[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

@@

for(i in 1:dim(res_hassell_local)[3]){
  s<-res_hassell_local[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

@@

for(i in 1:dim(res_hassell_global)[3]){
  s<-res_hassell_global[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

@@

for(i in 1:dim(res_msmith_local)[3]){
  s<-res_msmith_local[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

@@

for(i in 1:dim(res_msmith_global)[3]){
  s<-res_msmith_global[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

@@

for(i in 1:dim(res_pennycuick_local)[3]){
  s<-res_pennycuick_local[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

@@

for(i in 1:dim(res_pennycuick_global)[3]){
  s<-res_pennycuick_global[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

@@

for(i in 1:dim(res_verhulst_local)[3]){
  s<-res_verhulst_local[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

@@

for(i in 1:dim(res_verhulst_global)[3]){
  s<-res_verhulst_global[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

@@

for(i in 1:dim(res_abrewer_local)[3]){
  s<-res_abrewer_local[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

@@

for(i in 1:dim(res_abrewer_global)[3]){
  s<-res_abrewer_global[,,i]
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=c(0,1),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

>>>>

for(i in 1:dim(res_ricker_local)[3]){
  #s<-res_ricker_local[,,i]
  s<-res_ricker_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))

@@

for(i in 1:dim(res_ricker_global)[3]){
  #s<-res_ricker_global
  s<-res_ricker_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

@@

for(i in 1:dim(res_hassell_local)[3]){
  s<-res_hassell_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

@@

for(i in 1:dim(res_hassell_global)[3]){
  s<-res_hassell_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

@@

for(i in 1:dim(res_msmith_local)[3]){
  s<-res_msmith_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

@@

for(i in 1:dim(res_msmith_global)[3]){
  s<-res_msmith_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

@@

for(i in 1:dim(res_pennycuick_local)[3]){
  s<-res_pennycuick_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

@@

for(i in 1:dim(res_pennycuick_global)[3]){
  s<-res_pennycuick_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

@@

for(i in 1:dim(res_verhulst_local)[3]){
  s<-res_verhulst_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

@@

for(i in 1:dim(res_verhulst_global)[3]){
  s<-res_verhulst_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```

@@

for(i in 1:dim(res_abrewer_local)[3]){
  s<-res_abrewer_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()

@@

for(i in 1:dim(res_abrewer_global)[3]){
  s<-res_abrewer_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=1.5,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
         col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)))
}
par(op)
dev.off()
```
